Seismic Hazard Estimation of Northern Iran Using Smoothed Seismicity

### 2016-07-05 results.tex
preparing figure 11

Using the data, parameters, and procedures described above, we considered different hazard models based on whether we use the five distinct seismic hazard regions or the whole region of interest as a uniform seismic hazard region. We call these the R and U models, respectively. We also considered two threshold levels of ground motion for events exceeding magnitudes $M_w$ 5.5 and 6.5. We refer to these models with the suffixes 5.5 and 6.5, respectively. Each of these are considered under two probabilities of exceedance, at 2 and 10 percent in 50 years, for which we use the prefixes 2 and 10, respectively. As an example, we refer to the results for 2 percent probability of exceeding an event magnitude $M_w$ 5.5 in 50 years under the five seismic regions model as the 2R5.5 model results.

In the R models, we computed the probability of exceedance of the ground motion separately for each region and then add them together in order to have the contribution of all regions for any given grid point within the region of interest. The results are obtained in the form of annual rate of exceedance. Expected PGA values are therefore a slice or snapshot of the actual hazard curves of each point for any chosen magnitude.

We extract expected levels of ground motion for the two magnitude models, 5.5 and 6.5, based on the assumption that buildings of different construction systems may be vulnerable to different magnitude earthquakes. It is natural to anticipate that modern constructions in urban areas in Iran follow current building regulations and are thus well-designed to withstand moderate magnitude earthquakes $M_w$ 4.5--6.5, and to undergo moderate non-life threatening damage during $M_w > 6.5$ events. Unconventional constructions in poor city outskirts, rural housing and historical buildings may, however, be vulnerable to $M_w \leq 5.5$, and thus becomes relevant to entertain lower magnitude exceedance levels. In turn, the 2 and 10 percent probability of exceedance in a 50-years span are considered a standard practice in seismic design \citep[e.g.,][]{BHRC2014}.

@@

These, of course, are only mean expected levels of ground motion. A more complete picture is captured when considering statistical deviations. Fig.~\ref{fig:pgastd} shows again the mean PGA for the models 2R6.5 and 10R6.5, but this time along with the marginal values of plus and minus one standard deviation. Here, the standard deviation is carried forward in the calculation from the attenuation relationship and thus affects every grid point differently depending on the added contributions from each region. The highest expected PGA values are observed in the 2R6.5+STD model with accelerations of higher than 1 g in the Kopeh Dagh region and west of Tehran, and 0.8 g south of the North Tabriz Fault system and in the Zagros region along.

>>>>

Using the data, parameters, and procedures described above, we considered different hazard models based on whether we use the five distinct seismic hazard regions or the whole area of interest as a uniform seismic hazard region. We call these the R and U models, respectively. We also considered two threshold levels of ground motion for events exceeding magnitudes $M_w$ 5.5 and 6.5. We refer to these models with the suffixes 5.5 and 6.5, respectively. Each of these are considered under two probabilities of exceedance, at 2 and 10 percent in 50 years, for which we use the prefixes 2 and 10, respectively. These probabilities correspond to return periods of 475 and 2475 years. As an example of the chosen nomenclature, we refer to the results for 2 percent probability of exceeding an event magnitude $M_w$ 5.5 in 50 years under the five seismic regions model as the 2R5.5 model results.

In the distinct regions R models, we computed the probability of exceedance of the ground motion separately for each region and then add them together in order to have the contribution of all regions for any given grid point within the region of interest. The results are obtained in the form of annual rate of exceedance. Expected PGA values are therefore a slice of the actual hazard curves cut across all grid points for a chosen magnitude.

We extract expected levels of ground motion for magnitudes 5.5 and 6.5, based on the assumption that buildings of different construction systems may be vulnerable to different magnitude earthquakes. It is natural to anticipate that modern constructions in urban areas in Iran follow current building regulations and are thus well-designed to withstand moderate magnitude earthquakes $M_w$ 4.5--6.5, and to undergo moderate non-life threatening damage during $M_w > 6.5$ events. Unconventional constructions in poor city outskirts, rural housing and historical buildings may, however, be vulnerable to $M_w \leq 5.5$, and thus becomes relevant to entertain lower magnitude exceedance levels. In turn, the 2 and 10 percent probability of exceedance in a 50-years span are considered a standard practice in seismic design \citep[e.g.,][]{BHRC2014}.

@@

These, of course, are only mean expected levels of ground motion. A more complete picture is captured when considering statistical deviations. Fig.~\ref{fig:pgastd} shows again the mean PGA for the models 2R6.5 and 10R6.5, but this time along with the marginal values of plus and minus one standard deviation. Here, the standard deviation is carried forward in the calculation from the attenuation relationship and thus affects every grid point differently depending on the added contributions from each region.

The highest expected PGA values are observed in the 2R6.5+STD model with accelerations of higher than 1 g in the Kopeh Dagh region and west of Tehran, and 0.8 g south of the North Tabriz Fault system and in the Zagros region along. These maximum values should, nonetheless, be interpreted with caution given the fact that predictions are based on rock-site assumptions and do not include any kind of site effects, such as inelastic deformation of near-surface geotechnical layers which may often contribute to mitigate peak accelerations.

An additional consideration to make here is the fact that one cannot claim any of the models to be uniquely correct. They all carry a certain level of epistemic uncertainty which make them equally accurate and inaccurate at the same time. An means to reduce the overall uncertainty intrinsically associated with each model is to use combinations of different models. We consider two types of combinations here to aid our analysis. First, we combine results at both magnitude thresholds following the hypothesis that in areas were mixed reinforced and unreinforced buildings are present, the hazard and associated expected ground motions will be an average of both models, i.e. $frac{1}{2}(5.5+6.5)$. Second, we consider a combination of the five-regions model and the uniform model, i.e. $frac{1}{2}(\mathrm{U}+\mathrm{R})$, based on the hypothesis that both models carry forward valid information about the local and regional seismicity.

Fig.~\ref{fig:}a shows
